Cheat Sheet for PFPL

### 2016-08-21 pfpl/draftcheatsheet.tex
Add new chapter

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

@@

>>>>

\subsubsection*{32 Fluid Binding}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\
78 & 290 & $\mu ' \otimes a \hookrightarrow e$ & Tensor product & Extended by &  Map symbol $a$ to expression $e$\\
79 & 290 & $\mu ' \otimes a \hookrightarrow \bullet$ & Tensor product & Extended by &  Symbol $a$ is undefined\\
80 & 290 & $\mu ' \otimes a \hookrightarrow $ \underline{ } & Tensor product & Extended by &  Symbol $a$ is indeterminate\\

@@

81& 308 & $x \leftarrow e ; m$ & Left arrow & Sequence & Execute command $m$ with $e$ substituted for $x$ \\
82& 308 & $a := e$ & Colon equals & Assign & Assign $e$ to $a$\\
83 & 308 & $*a$ & Star & Contents & Get the value of $a$\\
84 & 309 & $ m \| \mu $& State & State & Command $m$ with memory map $\mu$\\
85 & 314 & $ m \thicksim \tau$ & Dotted tilde & Dotted tilde & Command $m$ returns a value of type $\tau$\\
\end{tabular}

\subsubsection*{35 Assignable References}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

86 & 320 & $ \& a $ & Ampersand & Reference & Reference to assignable \\

\subsubsection*{36 Lazy Evaluation}
\begin{tabular}[b] {p{.025\textwidth} p{.025\textwidth} p{.13\textwidth} p{.15\textwidth} 
p{.22\textwidth} p{.32\textwidth}}
N & P & Expression & Name & Say & Meaning \\ \\

87 & 333 & $ \Longrightarrow $ & Long right arrow & Implies & Implication (low precedence) \\
